DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-25 paper/main.tex
intro revision

In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are very
affordable. The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN), which has 9
layers, about 27 million connections and 250 thousand parameters
(weights). The network architecture is in fact identifical to the one
used in Nvidia's DAVE-2 self-driving car~\cite{Bojarski2016}. Other
than the obvious difference in scale (RC car vs. real car), from the 
perspective of computing systems, the only differences between
our system and Nvidia's DAVE-2 are that our system is implemented in
TensorFlow~\cite{abadi2016tensorflow} and runs on a 
Raspberry Pi 3 whereas Nvidia's DAVE-2 systems is implemented in Torch
7~\cite{collobert2011torch7} and runs on a Drive PX self-driving car
computer~\cite{drivepx}, which is much more powerful but also a lot more
expensive.

@@

By creating and using the Picar platform, we seek to accomplish the
following three goals. First, the significant reduction of the overall cost required
would make autonomous driving research more accessible to interested
individuals/parties. Furthermore, it would remove the concerns of
creating replacement platforms as each part, or the entire system,
could be replaced relatively inexpensively. Second, the utilization of
a more cost-efficient platform would allow for a better understanding
of the performance requirements necessary for efficiently operating
autonomous vehicles. Finally, we strive to achieve the ability to
compare the real-time performance of multiple embedded computing
platforms.

We display the efficacy of the Picar by training and testing the
DeepTesla DNN \cite{} in a custom-made environment. We find that the
Picar is capable of consistently accomplishing all real-time
operations required for autonomous driving in a 50 millisecond frame.

>>>>

In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera, as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network is deep as it has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is in fact identifical to the one
used in Nvidia's DAVE-2 self-driving car~\cite{Bojarski2016}. Other
than the obvious difference in scale (RC car vs. real car), from the
computing perspective, the only differences between
the two systems are that our system is implemented in
TensorFlow~\cite{abadi2016tensorflow} and runs on a 
Raspberry Pi 3 whereas Nvidia's DAVE-2 systems is implemented in Torch
7~\cite{collobert2011torch7} and runs on a Drive PX computer (NVIDIA's
automotive specialized computing system~\cite{drivepx}), which is more
powerful but also more expensive.

We follow the standard supervised learning methodology to train the
system with a goal of following lanes on the ground, mimicking real
roads. We first collected data for taining and validation by manually 
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a Nvidia GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each \emph{inference} operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)

The primary {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present the design, implementation, and case-study of a low-cost
    autonomous vehicle that utilizes the state-of-the-art aritificial 
    intelligence techniques.
  \item We systematically analyze real-time characteristics of
    multiple embedded computing platform, including the Raspberry Pi 3
    Model B, in the contex of a vision-based autnomous driving.
\end{itemize}

@@

%% By creating and using the Picar platform, we seek to accomplish the 
%% following three goals. First, the significant reduction of the overall
%% cost required 
%% would make autonomous driving research more accessible to interested
%% individuals/parties. Furthermore, it would remove the concerns of
%% creating replacement platforms as each part, or the entire system,
%% could be replaced relatively inexpensively. Second, the utilization of
%% a more cost-efficient platform would allow for a better understanding
%% of the performance requirements necessary for efficiently operating
%% autonomous vehicles. Finally, we strive to achieve the ability to
%% compare the real-time performance of multiple embedded computing
%% platforms.

%% We display the efficacy of the Picar by training and testing the
%% DeepTesla DNN \cite{} in a custom-made environment. We find that the
%% Picar is capable of consistently accomplishing all real-time
%% operations required for autonomous driving in a 50 millisecond frame.
